|

### 2024-04-16 Drafts/Paper_1/01-analysis_no_age_correction.Rmd
Update with age and no age correction
Revised to run the model without using the age-correction (i.e., model without going to age 0, which should work fine since fecundity of anything smaller than recruits is effectively 0 for basically all the stocks).  Results very similar to the 'age corrected' analysis.  A few minor bug fixes as well.  Also have part of the methods written.

---
title: "ICM testing"
output:
  pdf_document: default
  html_document: default
  word_document: 
    #reference_docx: template.docx
editor_options:
  chunk_output_type: console
---

The data is now available to test this on at least 81 stocks.  All of the NE Atlantic stocks (ICES) have been through the QA/QC process and we are happy with those data (Sept 1, 2022).  Let's see if we can get this to work on all the stocks with sufficient data...

```{r, load-stuff,echo=F, message=F, warning=F, fig.width=6, fig.height=4}
# OK, so using the ICES assessments here's what we get for North Sea cod.
library(readxl)
library(tidyverse)
library(rio)
library(ggthemes)
library(cowplot)
library(gtable)
library(viridis)
loc <- 'D:/GitHub/ICM'

source(paste0(loc,"/Scripts/functions/tuning_sim_fast.R"))

# Choose 5 ICES stocks that we have the necessary data for
#ASR <- read_xlsx("../Data/ASR_2018.xlsx" sheet = "ICES")
ASR1 <- read.csv(paste0(loc,"/Data/ICM_data_NE_atlantic_stocks.csv"))
ASR <- read.csv(paste0(loc,"/Data/ICM_data_NW_atlantic_stocks.csv"))

ASR <- rbind(ASR1,ASR)
datatypes <- unique(gsub(x = names(ASR), pattern = "[^a-zA-Z]", replacement=""))

# Replace 0's in Num.tot with NA so the rest of this works as Freya designed it to...
ASR$Num.tot[ASR$Num.tot == 0] <- NA
# we want:
# Year, Num, WA, Catch, AM, NM, StockID, Management, Area, Order, Family, Genus, Species
ASRdat <- ASR[,c(grep(x=names(ASR), "Num"),
                 grep(x=names(ASR), "WA"),
                 grep(x=names(ASR), "Catch"),
                 grep(x=names(ASR), "AM"),
                 grep(x=names(ASR), "NM"))]
# Making all the data numeric that should be numeric
ASRdat <- apply(X = ASRdat, 2, as.numeric)
# Getting the species info back
ASRsp <- ASR[, which(!1:length(names(ASR)) %in% grep(x=names(ASR), ".", fixed=T))]
# And binding it all back together
ASR_trim <- cbind(ASRsp, ASRdat)
# need a unique ID for stock
#table(ASR_trim$Management, ASR_trim$Species)
ASR_trim$Stock <- paste0(ASR_trim$Management, "_", ASR_trim$Area, "_", ASR_trim$Genus, "_", ASR_trim$Species)

ASR_long <- ASR_trim %>%
  pivot_longer(!c("Management", "Area", "Order", "Family", "Genus", "Species", "Stock", "Year","Meeting_or_reference","Model","Case","Notes")) %>%
  separate(col=name, into=c("type", "age"), sep = "\\.")

# Something is weird with the mentella stock, I'm going to drop it...
ASR_long <- ASR_long %>% dplyr::filter(Stock != "ICES-AFWG_DEEP1-2_Sebastes_mentella")

```{r, prep-data,echo=F, message=F, warning=F, fig.width=6, fig.height=4}

Stocks <- ASR_long %>%
                    dplyr::filter(!is.na(value)) %>%
                    dplyr::group_by(Stock, type) %>%
                    dplyr::summarize(count=length(unique(value))) %>%
                    dplyr::group_by(Stock) %>%
                    dplyr::summarize(types=length(unique(type))) %>%
                    dplyr::filter(types==5) %>%
                    dplyr::select(Stock)

@@

# Stocks <- ASR_stocks %>%
#                       dplyr::group_by(Stock, Species, type) %>%
#                       dplyr::summarize(ages=length(unique(age)),
#                                 years=length(unique(Year))) %>%
#                       dplyr::arrange(-years, -ages) %>%
#                       dplyr::filter(!Species=="morhua") %>%
#                       dplyr::distinct(Stock) %>%
#                       dplyr::pull(Stock)
# 
# print(Stocks)
Stocks <- Stocks$Stock

# Going to remove Sebastes norvegicus because we can't get fecundity as the only data we have is total numbers.
#Stocks <- Stocks[Stocks != "ICES-AFWG_DEEP1-2_Sebastes_norvegicus"]
# Esmarki doesn't work great as it is assessed using a quarterly model.
#Stocks <- Stocks[Stocks != "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii"]
#i = 'ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus'
years.tmp <- NULL
pnm.tmp <- NULL
waa.tmp <- NULL
ages.tmp <- NULL
rem.tmp <- NULL
mx.tmp <- NULL
NE.tmp <- NULL
vpa.tmp <- NULL
am.tmp <- NULL
mr.tmp <- NULL
all.abund.tmp <- NULL
full.abund.tmp <- NULL
full.rem.tmp <- NULL
fs.tmp <- NULL
for(i in Stocks)
{
  print(i)
  ASR_sub <- ASR_long %>%
    dplyr::select(Year, Stock, type, age, value) %>%
    dplyr::filter(Stock==i)

  # Drop the NA years....
  if(i == "ICES-NWWG_ICE-Summer_Clupea_harengus") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1986)
  # There's some funkiness going on in the first 7 years of these data, so staring in year 8
  if( i == "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1971)
  if(i == "ICES-NWWG_FA5b_Pollachius_virens") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1982)
  if(i == "ICES-NWWG_FA5a_Pollachius_virens") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1984)
  if(i == "ICES-AFWG_NEA1-2_Pollachius_virens") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1969)
  if(i == "ICES-WGCSE_CS27.6a_Merlangius_merlangus") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1980)
  if(i == "ICES-WGCSE_NS6a_Gadus_morhua") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1980)
  if(i == "ICES-AFWG_COASTNOR 1-2_Gadus_morhua") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 2006)
  if(i == "NEFSC_5Z_Pseudopleuronectes_americanus") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1982)
  if(i == "ICES-WGNSSK_NS 4-7d_Merlangius_merlangus") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1989)

  # maxage <- max(as.numeric(ASR_sub$age[!is.na(ASR_sub$value)]))
  # maxYear <- max(ASR_sub$Year[!is.na(ASR_sub$value)])
  # minYear <- min(ASR_sub$Year[!is.na(ASR_sub$value)])
  # forplot <- ASR_sub[as.numeric(ASR_sub$age) < (maxage+1) & ASR_sub$Year %in% minYear:maxYear,]
  # 
  # # summary plots
  # print(ggplot() + geom_line(data=forplot, aes(Year, value)) + facet_grid(type~as.numeric(age), scales="free_y") +
  #         geom_vline(data=forplot[is.na(forplot$value),], aes(xintercept=Year), colour="red") + facet_grid(type~as.numeric(age), scales="free_y") +
  #         theme_bw() + 
  #         ggtitle(i)
  # )

  age.mat <- ASR_sub %>% dplyr::filter(type=="AM") %>% dplyr::rename(AM=value) %>% dplyr::select(-type)
  # All of the age at maturities are NA in 0 and 1 year olds, so make them 0's, do that carefully just
  # in case that changes later...
  am.0s <- length(which((!is.na(age.mat$AM[age.mat$age ==0]))))
  am.1s <- length(which((!is.na(age.mat$AM[age.mat$age ==1]))))
  am.2s <- length(which((!is.na(age.mat$AM[age.mat$age ==2]))))
  am.3s <- length(which((!is.na(age.mat$AM[age.mat$age ==3]))))
  if(am.0s == 0) age.mat$AM[age.mat$age ==0] <- 0
  if(am.1s == 0) age.mat$AM[age.mat$age ==1] <- 0
  if(am.2s == 0) age.mat$AM[age.mat$age ==2] <- 0
  if(am.3s == 0) age.mat$AM[age.mat$age ==3] <- 0

   # Now we can get the abundance from the VPA models
  abund <- ASR_sub %>% dplyr::filter(type=="Num") %>% dplyr::rename(Num=value) %>% dplyr::select(-type)

  #if(am.1s | am.0s | am.2s > 0) print("Stop, you need to check the age at maturity for either age 0 or 1 as there is data in there.")
  # Now do something similar for the Natural moralities, but in this case
  # we take the NM of the youngest age class we have information for and back that number up to year 0.
  # DK NOTE:  THIS IS A BIG CHANGE IN DIRECTION FOR THE LOTKA CALCS SO NEED TO NOTE THIS ONE!!

  nm.tmp <-  ASR_sub %>% dplyr::filter(type=="NM") %>% dplyr::rename(NM=value) %>% dplyr::select(-type)

  #minage
  minage <- min(as.numeric(nm.tmp$age[!is.na(nm.tmp$NM)]))
  if(minage == 0)  nat.mort <- nm.tmp
  # Some specials...
  if(i %in% c("ICES-WGCSE_CS7e-k_Gadus_morhua","ICES-WGCSE_ROCK6b_Melanogrammus_aeglefinus",
              "ICES-WGHANSA_SP8abd_Sardina _pilchardus","ICES-WGWIDE_NEA 1-9,12,14_Micromesistius_poutassou")) minage <- 1
  if(i == "ICES-WGWIDE_NEA 1,2,5,4a,14a_clupea_ harengus") minage <- 2
  #maxage
  maxage <- max(as.numeric(nm.tmp$age[!is.na(nm.tmp$NM)]))

  # Now get the number of individuals in the youngest age category
  num.age.min <- ASR_sub %>% dplyr::filter(age==minage,type=="Num")
  # So any Recruitment even that is > 3 SE's away from the median I'm calling 
  # an 'extreme' recruitment event and it is going to get a lower/higher natural mortality term.
  med.mun.age.min <- mean(num.age.min$value,na.rm=T)
  sd.mun.age.min <- sd(num.age.min$value,na.rm=T)#/sqrt(length(na.omit(num.age.min$value)))
  low.rec <- med.mun.age.min - 2*sd.mun.age.min
  high.rec <- med.mun.age.min + 2*sd.mun.age.min
  high.rec.years <- as.vector(na.omit(num.age.min$Year[num.age.min$value > high.rec]))
  low.rec.years <- as.vector(na.omit(num.age.min$Year[num.age.min$value < low.rec]))
  # Set up the full abundance matrix 
  full.abund <- abund
  print(paste0("Stock ", i , ' high recruit years include ', length(c(low.rec.years,high.rec.years)), ' years'))
  # If we need to imput some data run this loop for natural mortality
  if(minage == 0) full.abund <- abund

  if(minage > 0)
  {
    yrs <- sort(unique((nm.tmp$Year)))
    nm.res <- NULL
    # These already have NM estimates at 0 so don't need to do them...
    if(!i %in% c("ICES-WGCSE_CS7e-k_Gadus_morhua","ICES-WGCSE_ROCK6b_Melanogrammus_aeglefinus",
                 "ICES-WGHANSA_SP8abd_Sardina _pilchardus","ICES-WGWIDE_NEA 1,2,5,4a,14a_clupea_ harengus",
                 "ICES-WGWIDE_NEA 1-9,12,14_Micromesistius_poutassou"))
    {
      # Just use the mean mortality of the youngest age class we have information for
      nm.use <- mean(nm.tmp$NM[nm.tmp$age==minage],na.rm=T)
      # Take the average natural mortality of the youngest age class with an m and use that
      # This avoids really blowing up the abundance in the younger age classes which can get a bit squirrly
      # nm.high.rec <- 0.5*(min(nm.tmp$NM[nm.tmp$age==minage],na.rm=T))
      # nm.low.rec <-  1.5*(max(nm.tmp$NM[nm.tmp$age==minage],na.rm=T))
      # Start by filling in everything...
      nm.tmp$NM[is.na(nm.tmp$NM)] <- nm.use
      nm.tmp <- nm.tmp[nm.tmp$age %in% 0:maxage,]
      # Now we need to fill in the 'special' cohorts that were really big (low m) or really small (high m)
      # for(y in length(yrs):1)
      # {
      #   if(yrs[y] %in% c(high.rec.years,low.rec.years))
      #   {
      #     if(yrs[y] %in% high.rec.years) nm.pick <- nm.high.rec
      #     if(yrs[y] %in% low.rec.years) nm.pick <- nm.low.rec
      #     for(a in minage:1) nm.tmp$NM[nm.tmp$Year == (yrs[y]-a) & nm.tmp$age == minage-a] <- nm.pick
      # }} #Close the if and for loops
      # Pointless rename...
    } #end the skip the stocks with nm at 0 if
      nat.mort <- nm.tmp

  # Now do the same loopiness for abundance
    for(y in length(yrs):2)
    {
      # The minage of the natural mortality is different from minage of the abundance, annoyingly for this stock...
      if(i == "ICES-AFWG_NEA1-2_Gadus_morhua") minage <- 3
      if(i == "ICES-NWWG_ICE-Summer_Clupea_harengus") minage <- 3

           # The lowest minage =4, This goes first since we go backwards, this gets us age 3 in year 3
           if(minage ==4) 
           {
               four.abund <- full.abund %>% dplyr::filter(Year == yrs[y], age == 4) %>% dplyr::pull(Num)
               nm.four <- 1-exp(-nat.mort[nat.mort$Year ==yrs[y]-1,][4,]$NM) 
               full.abund[full.abund$Year ==yrs[y]-1,][4,]$Num <- four.abund/(1-nm.four)
             #}# end my 2:0
           } # end if minage ==4

            # The minage =3 scenario, goes after 4...
           if(minage >=3)
           {
             # for(my in 0:1)
             # {
               three.abund <- full.abund %>% dplyr::filter(Year == yrs[y], age == 3) %>% dplyr::pull(Num)
               nm.three <- 1-exp(-nat.mort[nat.mort$Year ==yrs[y]-1,][3,]$NM) 
               full.abund[full.abund$Year ==yrs[y]-1,][3,]$Num <- three.abund/(1-nm.three)
             #} # end my 1:0
           } # end if(minage ==2)

           # The minage =2 scenario, this goes last
           if(minage >=2)
           {
             two.abund <- full.abund %>% dplyr::filter(Year == yrs[y], age == 2) %>% dplyr::pull(Num)
             nm.two <- 1-exp(-nat.mort[nat.mort$Year ==yrs[y]-1,][2,]$NM) 
             full.abund[full.abund$Year ==yrs[y]-1,][2,]$Num <- two.abund/(1-nm.two)
           } # end if(minage ==2)

           if(minage >=1)
           {
             one.abund <- full.abund %>% dplyr::filter(Year == yrs[y], age == 1) %>% dplyr::pull(Num)
             nm.one <- 1-exp(-nat.mort[nat.mort$Year ==yrs[y]-1,][1,]$NM) 
             full.abund[full.abund$Year ==yrs[y]-1,][1,]$Num <- one.abund/(1-nm.one)
           } # end if(minage ==2)

         } # The annoying if to fill in rest of the first few years.
  } # end if minage > 0

  # We won't have a weight at age for the young ages, which is fine since we only need that for SSB
  weight.age <- ASR_sub %>% dplyr::filter(type=="WA") %>% dplyr::rename(WA=value) %>% dplyr::select(-type)
  removals <- ASR_sub %>% dplyr::filter(type=="Catch") %>% dplyr::rename(Catch=value) %>% dplyr::select(-type)
  # Fill the leading NAs with 0s now...
  if(minage > 0) 
  {
    weight.age$WA[weight.age$age %in% 0:(minage-1)] <- 0
    removals$Catch[removals$age %in% 0:(minage-1)] <- 0
  }
 # if(i=="ICES-WGBFAS_BS 22-32_Sprattus_sprattus") removals$Catch <- removals$Catch/1000

  data <- age.mat %>%
    full_join(nat.mort) %>%
    #full_join(abund) %>%
    full_join(full.abund) %>%
    full_join(weight.age) %>%
    full_join(removals)

  # Nice way to toss NAs!
  data$available <- apply(is.na(data[, c("AM", "Num", "WA")]), 1, function(x) all(!x==T))
  data <- data[data$available==T,]
  # And then toss the years we don't have 0 data for Numbers in the 0 age class
  toss.years <- data %>% dplyr::group_by(Year) %>% dplyr::reframe(bad.years = which(min(age)>0))
  data <- data[!data$Year %in% toss.years$Year,]

@@

  N.end <- sum(data[data$Year==max(years),]$Num)
  all.abund <- data %>% dplyr::group_by(Year) %>% dplyr::summarize(vpa=sum(Num,na.rm=T)) %>% pull(vpa)
  vpa.abund <- data %>% dplyr::group_by(Year) %>% dplyr::filter(age %in% minage:maxage) %>% dplyr::summarize(vpa=sum(Num,na.rm=T)) %>% pull(vpa)
  # The real mx matrix, recruits produced per individual in each age class... Not perfect as I need to offset recruits/ssb, but close enough for the moment..

  #recruits
  annual <- data.frame(Year=data$Year[data$age==0], recruits=data$Num[data$age==0])
  #ssn
  data$ssn <- data$Num * data$AM
  #ssb
  data$ssb <- data$ssn * data$WA #I need to figure out how to line this up with the number of recruits for the right years in the data object.... got it right for the overall r.p.ssb below.
  #tot.ssb
  annual <- data %>% group_by(Year) %>% summarize(tot.ssb = sum(ssb)) %>% left_join(annual)

@@

  #r.p.ssb So we are assuming the SSB in year X produces the observed recruits in year X
  annual$r.p.ssb <- annual$recruits/annual$tot.ssb
  # recs.per.age
  data <- left_join(data, annual)
  # So I need to make an offset SSB in the 'data' object to line up with the correct r.p.ssb field.  This is probably gonna suck...
  # tmp <- NULL
  # for(j in 1:length(years))
  # {
  #   tst <- data %>% dplyr::filter(Year == years[j]) %>% dplyr::select(ssb,ssn,Year,age)
  #   tst$Year <- tst$Year + minage
  #   names(tst) <- c("ssb.offset","ssn.offset","Year","age")
  #   tmp[[j]] <- tst
  # }
  # Unpack the list
  #@ssb.off <- do.call('rbind',tmp)
  # And merge it with the data object
  #data <- left_join(data,ssb.off,by=c("Year","age"))
  data$recs.per.age <- data$ssb*data$r.p.ssb
  # mx
  # Some of the stocks are just the males and females, so these are already half the population.  Probably can just not include the male stocks in the end.
  # The demographic models are 'female' only, so we'd want to divide the number of recruits by 2 and the SSN by 2, but that just cancels out
  # so there is no need to make the mom adjustment.
  data$mx <- data$recs.per.age/data$ssn # if(grepl("males",i))
  # if(!grepl("males",i))data$mx <- data$recs.per.age/data$ssn/2 # Moms only! 
  data$mx[is.nan(data$mx)] <- 0 # if we don't have any spawners in an age class in a year their fecundity is 0
  # Now for the very high recruitment years allow for a small amount of recruitment (20% of the lowest age) in the age classes after year 0....

  # if(length(high.rec.years) > 0)
  # {
  #   for(y in high.rec.years)
  #   {
  #     tmp <- data$AM[data$Year == y]
  #     am.fill <- which(tmp ==0) 
  #     if(length(am.fill) > 1) data$mx[data$Year == y-1][am.fill[-1]] <- 0.2*min(data$mx[data$Year == y & data$mx > 0],na.rm=T)
  #   }
  # }

  age.mat <- data %>% dplyr::select("Year", "age", "AM") %>% pivot_wider(names_from=age, values_from = AM) %>% dplyr::select(-Year)
  prop.nat.mort <- data %>% dplyr::select("Year", "age", "prop.nat.mort") %>% pivot_wider(names_from=age, values_from = prop.nat.mort) %>% dplyr::select(-Year) %>% as.data.frame
  weight.age <- data %>% dplyr::select("Year", "age", "WA") %>% pivot_wider(names_from=age, values_from = WA) %>% dplyr::select(-Year)
  mx <- data %>% dplyr::select("Year", "age", "mx") %>% pivot_wider(names_from=age, values_from = mx) %>% dplyr::select(-Year) %>% as.data.frame()
  abund.age <- data %>% dplyr::select("Year", "age", "Num") %>% pivot_wider(names_from=age, values_from = Num) %>% dplyr::select(-Year) %>% as.data.frame()
  # Now we can save out the catch and get an instantaneous F
  data$Catch[is.na(data$Catch)] <- 0
  data$Exp <- data$Catch/data$Num
  # If it is exactly 1 that leads to an Inf, which is annoying, so make it 1.1 and fix it with the rest below
  data$Exp[data$Exp == 1] <- 1.1
  # And make this an F
  data$Fs <- -log(1-data$Exp)
  if(any(is.na(data$Fs)))
  {
    fixers <- which(is.na(data$Fs))
    print(paste0("Had to replace ",length(fixers), ' exploitation rates for stock ',i))
    for(f in fixers)
    {
      yr <- data$Year[f]
      fs <- max(data$Fs[data$Year == yr],na.rm=T)
      data$Fs[f] <- fs
      data$Exp[f] <- 1-exp(-fs)
    }
  }

@@

  if(i == "DFO_2J3KL_Gadus_morhua")
  {
    age.mat[,10:12] <- 1
    prop.nat.mort[,10:12] <- prop.nat.mort[,9]
    weight.age[12:14,11:12] <- weight.age[12:14,10]
    weight.age[15,12] <- weight.age[15,11]
    mx[12:14,11:12] <- mx[12:14,10]
    mx[15,12] <- mx[15,11]
    full.Fs[12:14,11:12] <- full.Fs[12:14,10]
    full.Fs[15,12] <- full.Fs[15,11]
    abund.age[12:14,11:12] <- abund.age[12:14,10]
    abund.age[15,12] <- abund.age[15,11]
    # I could calculate, but this will get us to the same place...
    full.rems[12:14,11:12] <- full.rems[12:14,10]
    full.rems[15,12] <- full.rems[15,11]
  }

  if(i == "DFO_4T-Spring_Clupea_harengus")
  {
    age.mat[6:7,12] <- 1
    prop.nat.mort[6:7,12] <- prop.nat.mort[6:7,11]
    weight.age[6:7,12] <- weight.age[6:7,11]
    mx[6:7,12] <- mx[6:7,11]
    full.Fs[6:7,12] <- full.Fs[6:7,11]
    abund.age[6:7,12] <- abund.age[6:7,11]
    full.rems[6:7,12] <- full.rems[6:7,11]
  }

  if(i == "ICES-HAWG_CS 6a- 7b-7c_Clupea_harengus") 
  {
    age.mat[30,9] <- 1
    prop.nat.mort[30,9] <- prop.nat.mort[30,8]
    weight.age[30,9] <- weight.age[29,9]
    mx[30,9] <- mx[30,8]
    full.Fs[30,9] <- full.Fs[30,8]
    abund.age[30,9] <- abund.age[30,8]
    full.rems[30,9] <- full.rems[30,8]
  }

>>>>

---
output: word_document
editor_options: 
  chunk_output_type: console
---

```{r, prep-data,echo=F, message=F, warning=F, fig.width=6, fig.height=4,include=F,message=F}

if(load.results==F)
{
  Stocks <- ASR_long %>%
                      dplyr::filter(!is.na(value)) %>%
                      dplyr::group_by(Stock, type) %>%
                      dplyr::summarize(count=length(unique(value))) %>%
                      dplyr::group_by(Stock) %>%
                      dplyr::summarize(types=length(unique(type))) %>%
                      dplyr::filter(types==5) %>%
                      dplyr::select(Stock)

@@

  # print(Stocks)
  Stocks <- Stocks$Stock

  # Going to remove Sebastes norvegicus because we can't get fecundity as the only data we have is total numbers.
  #Stocks <- Stocks[Stocks != "ICES-AFWG_DEEP1-2_Sebastes_norvegicus"]
  # Esmarki doesn't work great as it is assessed using a quarterly model.
  #Stocks <- Stocks[Stocks != "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii"]
  #i = 'ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus'
  years.tmp <- NULL
  pnm.tmp <- NULL
  waa.tmp <- NULL
  ages.tmp <- NULL
  rem.tmp <- NULL
  mx.tmp <- NULL
  NE.tmp <- NULL
  vpa.tmp <- NULL
  am.tmp <- NULL
  mr.tmp <- NULL
  abund.tmp <- NULL
  full.abund.tmp <- NULL
  full.rem.tmp <- NULL
  fs.tmp <- NULL
  for(i in Stocks)
  {
  print(i)
  ASR_sub <- ASR_long %>%
    dplyr::select(Year, Stock, type, age, value) %>%
    dplyr::filter(Stock==i)

    # Dropping the first 7 years as the 8 year olds are all missing
  if(i == "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus") ASR_sub <- ASR_sub |> collapse::fsubset(Year >= 1972)
  # maxage <- max(as.numeric(ASR_sub$age[!is.na(ASR_sub$value)]))
  # maxYear <- max(ASR_sub$Year[!is.na(ASR_sub$value)])
  # minYear <- min(ASR_sub$Year[!is.na(ASR_sub$value)])
  # forplot <- ASR_sub[as.numeric(ASR_sub$age) < (maxage+1) & ASR_sub$Year %in% minYear:maxYear,]
  # 
  # # summary plots
  # print(ggplot() + geom_line(data=forplot, aes(Year, value)) + facet_grid(type~as.numeric(age), scales="free_y") +
  #         geom_vline(data=forplot[is.na(forplot$value),], aes(xintercept=Year), colour="red") + facet_grid(type~as.numeric(age), scales="free_y") +
  #         theme_bw() + 
  #         ggtitle(i)
  # )

  age.mat <- ASR_sub %>% dplyr::filter(type=="AM") %>% dplyr::rename(AM=value) %>% dplyr::select(-type)
  # All of the age at maturities are NA in 0 and 1 year olds, so make them 0's, do that carefully just
  # in case that changes later...
  am.0s <- length(which((!is.na(age.mat$AM[age.mat$age ==0]))))
  am.1s <- length(which((!is.na(age.mat$AM[age.mat$age ==1]))))
  am.2s <- length(which((!is.na(age.mat$AM[age.mat$age ==2]))))
  if(am.0s == 0) age.mat$AM[age.mat$age ==0] <- 0
  if(am.1s == 0) age.mat$AM[age.mat$age ==1] <- 0
  if(am.2s == 0) age.mat$AM[age.mat$age ==2] <- 0

  #if(am.1s | am.0s | am.2s > 0) print("Stop, you need to check the age at maturity for either age 0 or 1 as there is data in there.")
  nat.mort <-  ASR_sub %>% dplyr::filter(type=="NM") %>% dplyr::rename(NM=value) %>% dplyr::select(-type)
  abund <- ASR_sub %>% dplyr::filter(type=="Num") %>% dplyr::rename(Num=value) %>% dplyr::select(-type)
  weight.age <- ASR_sub %>% dplyr::filter(type=="WA") %>% dplyr::rename(WA=value) %>% dplyr::select(-type)
  if(i == Stocks[30]) weight.age$WA <- weight.age$WA/1000
  removals <- ASR_sub %>% dplyr::filter(type=="Catch") %>% dplyr::rename(Catch=value) %>% dplyr::select(-type)

 # if(i=="ICES-WGBFAS_BS 22-32_Sprattus_sprattus") removals$Catch <- removals$Catch/1000

  data <- age.mat %>%
    full_join(nat.mort) %>%
    full_join(abund) %>%
    full_join(weight.age) %>%
    full_join(removals)

  # Aahh??  Is this NA dropping useful data, needed to quick fix the age at maturity data...
  data$available <- apply(is.na(data[, c("AM", "Num", "WA")]), 1, function(x) all(!x==T))
  data <- data[data$available==T,]

@@

  N.end <- sum(data[data$Year==max(years),]$Num)
  vpa.abund <- data %>% dplyr::group_by(Year) %>% dplyr::summarize(vpa=sum(Num,na.rm=T)) %>% pull(vpa)

  # The real mx matrix, recruits produced per individual in each age class... Not perfect as I need to offset recruits/ssb, but close enough for the moment..
  #minage
  minage <- min(as.numeric(data$age))
  #maxage
  maxage <- max(as.numeric(data$age))
  #recruits
  annual <- data.frame(Year=data$Year[data$age==minage], recruits=data$Num[data$age==minage])
  #ssn
  data$ssn <- data$Num * data$AM
  #ssb
  data$ssb <- data$ssn * data$WA #I need to figure out how to line this up with the number of recruits for the right years in the data object.... got it right for the overall r.p.ssb below.
  #tot.ssb
  annual <- data %>% group_by(Year) %>% summarize(tot.ssb = sum(ssb)) %>% left_join(annual)

@@

  #r.p.ssb This needs to be offset by the age of recruits
  annual$r.p.ssb <- c(rep(NA,minage),annual$recruits[(minage+1):nrow(annual)]/annual$tot.ssb[1:(nrow(annual)-minage)])
  # recs.per.age
  data <- left_join(data, annual)
  # So I need to make an offset SSB in the 'data' object to line up with the correct r.p.ssb field.  This is probably gonna suck...
  tmp <- NULL
  for(j in 1:length(years))
  {
    tst <- data %>% dplyr::filter(Year == years[j]) %>% dplyr::select(ssb,ssn,Year,age)
    tst$Year <- tst$Year + minage
    names(tst) <- c("ssb.offset","ssn.offset","Year","age")
    tmp[[j]] <- tst
  }
  # Unpack the list
  ssb.off <- do.call('rbind',tmp)
  # And merge it with the data object
  data <- left_join(data,ssb.off,by=c("Year","age"))
  data$recs.per.age <- data$ssb.offset*data$r.p.ssb
  # mx
  # Some of the stocks are just the males and females, so these are already half the population.  Probably can just not include the male stocks in the end.
  # No longer dividing by 2 because we should really divide recruits and ssn by 2 to be female only, but that's pointless so we roll along with this.
  data$mx <- data$recs.per.age/data$ssn.offset # if(grepl("males",i)) 
  #if(!grepl("males",i))data$mx <- data$recs.per.age/data$ssn.offset/2 # Moms only! 
  data$mx[is.nan(data$mx)] <- 0 # if we don't have any spawners in an age class in a year their fecundity is 0
  # Easier to remove the years where we don't have recs.per.age...
  #data <- data %>% dplyr::filter(Year %in% years[(minage+1):length(years)])
  # Something is wrong with the decline rate method, but the exponential and logistic are working pretty... pretty... pretty good...

  age.mat <- data %>% dplyr::select("Year", "age", "AM") %>% pivot_wider(names_from=age, values_from = AM) %>% dplyr::select(-Year)
  prop.nat.mort <- data %>% dplyr::select("Year", "age", "prop.nat.mort") %>% 
                            pivot_wider(names_from=age, values_from = prop.nat.mort) %>% 
                            dplyr::select(-Year) %>% as.data.frame

  weight.age <- data %>% dplyr::select("Year", "age", "WA") %>% pivot_wider(names_from=age, values_from = WA) %>% dplyr::select(-Year)
  mx <- data %>% dplyr::select("Year", "age", "mx") %>% 
                 pivot_wider(names_from=age, values_from = mx) %>% 
                 dplyr::select(-Year) %>% as.data.frame()
  # Get the abundance matrix
  abund.age <- data %>% dplyr::select("Year", "age", "Num") %>% 
                        pivot_wider(names_from=age, values_from = Num) %>% 
                        dplyr::select(-Year) %>% as.data.frame()

  # Now we can save out the catch and get an instantaneous F
    data$Catch[is.na(data$Catch)] <- 0
    data$Exp <- data$Catch/data$Num 
    # If it is exactly 1 that leads to an Inf, which is annoying, so make it 1.1 and fix it with the rest below
    data$Exp[data$Exp == 1] <- 1.1
    # And make this an F
    data$Fs <- -log(1-data$Exp)
    if(any(is.na(data$Fs)))
    {
      fixers <- which(is.na(data$Fs))
      print(paste0("Had to replace ",length(fixers), ' exploitation rates for stock ',i))
      for(f in fixers)
      {
        yr <- data$Year[f]
        fs <- max(data$Fs[data$Year == yr],na.rm=T)
        data$Fs[f] <- fs
        data$Exp[f] <- 1-exp(-fs)
      }
    }

@@

    if(i == "DFO_2J3KL_Gadus_morhua")
    {
      age.mat[,8:10] <- 1
      prop.nat.mort[,8:10] <- prop.nat.mort[,7]
      weight.age[12:14,9:10] <- weight.age[12:14,8]
      weight.age[15,10] <- weight.age[15,9]
      mx[12:16,9:10] <- mx[12:16,8]
      mx[17,10] <- mx[17,9]
      full.Fs[12:14,9:10] <- full.Fs[12:14,8]
      full.Fs[15,10] <- full.Fs[15,9]
      abund.age[12:14,9:10] <- abund.age[12:14,8]
      abund.age[15,10] <- abund.age[15,9]
      # I could calculate, but this will get us to the same place...
      full.rems[12:14,9:10] <- full.rems[12:14,8]
      full.rems[15,10] <- full.rems[15,9]
    }

    if(i == "DFO_4T-Spring_Clupea_harengus")
    {
      age.mat[6:7,10] <- 1
      prop.nat.mort[6:7,10] <- prop.nat.mort[6:7,9]
      weight.age[6:7,10] <- weight.age[6:7,9]
      mx[6:9,10] <- mx[6:9,9]
      full.Fs[6:7,10] <- full.Fs[6:7,9]
      abund.age[6:7,10] <- abund.age[6:7,9]
      full.rems[6:7,10] <- full.rems[6:7,9]
    }

    if(i == "ICES-HAWG_CS 6a- 7b-7c_Clupea_harengus") 
    {
      age.mat[30,8] <- 1
      prop.nat.mort[30,8] <- prop.nat.mort[30,7]
      weight.age[30,8] <- weight.age[29,8]
      mx[30:31,8] <- mx[30:31,9]
      full.Fs[30,8] <- full.Fs[30,7]
      abund.age[30,8] <- abund.age[30,7]
      full.rems[30,8] <- full.rems[30,7]
    }

    if(i == "ICES-WGCSE_IS6a-7b-7j_Dicentrarchus _labrax")
    {
      age.mat[c(14,27,40),5] <- age.mat[1,5]
      prop.nat.mort[c(14,27,40),5] <- prop.nat.mort[1,5]
      weight.age[c(14,27,40),5] <- weight.age[c(13,26,39),5]
      mx[c(14,16,27,29,40,42),5] <- mx[c(14,16,27,29,40,42),6]
      full.Fs[c(14,27,40),5] <- full.Fs[c(14,27,40),4]
      abund.age[c(14,27,40),5] <- abund.age[c(14,27,40),4]
      full.rems[c(14,27,40),5] <- full.rems[c(14,27,40),4]
    }
    # Clear out some 0's...
    if( i == "AFSC_EEBSAI_Limanda_aspera")
    {
      mx[5,18] <- mean(unlist(mx[5,c(17,19)]))
      mx[c(6,8),19] <- mx[c(6,8),18]
      mx[2:7,20] <- mx[2:7,19] 
    }
